---
title: "FirstKnitR"
author: "Carly"
date: "2/3/2022"
output:
  html_document: default
  word_document: default
  pdf_document: default
urlcolor: blue 
---
#**Advanced Topics in R: FW891**
##Class Four-- KnitR
###_Carly Andrews_

```{r setup, include=FALSE, cache = FALSE}
require("knitr")
## setting working directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

<!-- Runs the code but does not output to the document (include=FALSE) -->
```{r include=FALSE}
source(file="Scripts/ggp-app05.R");
```

The below code runs a math operation using the weather data which we used
in the homework. 

```{r include=TRUE}

weatherData$temp_range <- (weatherData$maxTemp)-(weatherData$minTemp)
mean <- mean(weatherData$temp_range)

```

We can also run this operation as an inline math equation:

The mean of the range of temperatures recorded is 'r mean(weatherData$temp_range'.

## Including Plots

You can also embed plots, for example:

```{r weatherData, echo=FALSE}
plot(scatter3)
```

We can also insert hyperlinks; for example, this <https://ggplot2.tidyverse.org/reference/element.html> is the website I used for homework four.

We can also create text formatting, including ~~strikethroughs~~.

